IRS-Aided SWIPT:\\Joint Waveform, Active and Passive Beamforming Design Under Nonlinear Harvester Model

### 2021-08-03 review/response_2.tex

			For GP Algorithm~\ref{M-al:gp}, the computational complexity is exponential w.r.t. the number of subbands \cite{M-Chiang2005}.
			\begin{framed}
				The joint waveform amplitude and splitting ratio design is summarized in the GP Algorithm~\ref{M-al:gp}, which achieves local optimality at the cost of exponential computational complexity \cite{M-Chiang2005}.
			\end{framed}

			For M-SCA Algorithm~\ref{M-al:m_sca}, each optimization problem involved is an SDP with $(L+1)$ variables and linear constraints, and the computational complexity is $\mathcal{O}\left(I_{\mathrm{M-SCA}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$ where $I_{\mathrm{M-SCA}}$ denotes the number of M-SCA iterations.
			\begin{framed}
				Compared with Algorithm~\ref{M-al:sca}, the rate constraint \eqref{M-co:irs_rate} is dropped and each SDP in Algorithm~\ref{M-al:m_sca} involves $(L+1)$ linear constraints. Given a solution accuracy $\epsilon_{\mathrm{IPM}}$ for the interior-point method, the computational complexity of Algorithm~\ref{M-al:m_sca} is $\mathcal{O}\left(I_{\mathrm{M-SCA}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{M-SCA}}$ denotes the number of M-SCA iterations \cite{M-Luo2010}. Note that $I_{\mathrm{M-SCA}}=1$ for the WIT point where no SCA is involved.
			\end{framed}

@@

			For BCD Algorithm~\ref{M-al:bcd}, since Algorithm~\ref{M-al:gp} is involved per iteration, the computational complexity is exponential w.r.t. the number of subbands.
			\begin{framed}
				The steps are summarized in the BCD Algorithm~\ref{M-al:bcd}, whose computational complexity is exponential as inherited from Algorithm~\ref{M-al:gp}.
			\end{framed}

			For LC-BCD Algorithm~\ref{M-al:lc_bcd}, both waveform and active beamforming are obtained in closed form, and the computational complexity of Algorithm~\ref{M-al:lc_bcd} is $\mathcal{O}\left(I_{\mathrm{LC-BCD}}I_{\mathrm{M-SCA}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{LC-BCD}}$ denotes the number of LC-BCD iterations \cite{M-Luo2010}.
			\begin{framed}
				Given a solution accuracy $\epsilon_{\mathrm{IPM}}$ for the interior-point method, the computational complexity of Algorithm~\ref{M-al:lc_bcd} is $\mathcal{O}\left(I_{\mathrm{LC-BCD}}I_{\mathrm{M-SCA}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{LC-BCD}}$ denotes the number of LC-BCD iterations \cite{M-Luo2010}.
			\end{framed}
			\label{re:1.1}
		\end{response}

		\begin{point}
			Since this paper focused on IRS-aided SWIPT systems, it could be better if the authors can further enrich the survey part to make the paper more comprehensive. In particular, some papers have considered this kind of problem from a different aspect such as \cite{Xu2021}. It is kindly suggested to briefly discuss the main difference between \cite{Xu2021} and the problem considered in this paper.
		\end{point}

		\begin{response}
			Thank you for sharing this paper. Instead of optimizing the phase shift of each IRS element, it tailored a tile-based two-stage optimization framework for large-scale IRS to enable a flexible performance-complexity tradeoff. The model also adapts well to practical IRS models accounting AoA and AoD. In contrast, our paper is more focused on waveform design and rate-energy tradeoff for one SWIPT user with practical co-located information decoder and energy harvester. We have updated the manuscript as follows.
			\begin{framed}
				In \cite{Xu2021}, the authors proposed a scalable resource allocation framework for SWIPT systems involving large-scale IRS, where the reflectors are grouped into tiles and the optimization process is divided into an offline mode-design stage and an online mode-selection stage. It was concluded that the proposed two-stage algorithm not only enables a flexible balance between performance and complexity but also adapts well to practical IRS and harvester models.

				\textellipsis To the best of our knowledge, all existing papers considered resource allocation and beamforming design for dedicated information and energy users in a single-carrier network. In this paper, we instead build our design based on a proper nonlinear harvester modeling that captures the dependency of the output DC power on both the power and shape of the input waveform, and marry the benefits of joint multi-carrier waveform and active beamforming optimization for SWIPT with the passive beamforming capability of IRS, to investigate the R-E tradeoff for one SWIPT user with practical co-located information decoder and energy harvester.
			\end{framed}
		\end{response}

@@

		\begin{point}
			It could be better if the authors can provide some references for the parameter values chosen in the simulation part.
		\end{point}

		\begin{response}
			The system layout follows \cite{M-Wu2019}. For the center frequency, we consider \SI{2.4}{\GHz} due to its ubiquitous and license-free properties. Note that the path loss can be greatly reduced (and the R-E performance can be improved) if the system operates at much lower frequency, as considered in most IRS papers. In the previous manuscript, we made a mistake in the choice of reference path loss. As indicated by Comment~\ref{pt:3.3}, even the free-space path loss should be around \SI{40}{\dB} at \SI{1}{\meter}. To fix this issue, we updated the path loss model as IEEE TGn channel model D that is representative of small environments such as residential homes and small offices \cite{M-Erceg2004}. It has three clusters with \SI{50}{\ns} r.m.s. delay spread, and the path loss exponent is set to \num{2} (i.e., free-space model) up to breakpoint distance \SI{10}{\meter} and set to \num{3.5} onwards. This has a similar effect to most IRS literatures that assign a relatively large path loss exponent to the direct path and smaller ones to the incident and reflected paths to penalize the channel with large distance. We also raise the EIRP from \SI{36}{\dBm} to \SI{40}{\dBm} (which still complies with FCC regulations \cite{Afar2021}) and change the receive antenna gain from \SI{2}{\dBi} to \SI{3}{\dBi}. As for the rectenna parameters, the parameters are taken from \cite{M-Clerckx2016a} and the reference have been added to the revised manuscript.
		\end{response}

@@

		\begin{point}
			The reviewer noticed that in Algorithm~\ref{M-al:lc_bcd}, there are two convergence criteria. It could be better if the authors can briefly interpret this issue.
		\end{point}

		\begin{response}
			We incorporated two cases (WIT/non-WIT) into Algorithm~\ref{M-al:lc_bcd}, where Algorithm~\ref{M-al:m_sca} is called during each iteration. To obtain the WIT point, the rate \eqref{M-eq:R_irs} instead of the DC current \eqref{M-eq:z_irs_approx} should be maximized, such that the current expression is dropped and no SCA is involved. To clarify this point, we have updated the description on Algorithm~\ref{M-al:m_sca} as follows.
			\begin{framed}
				To achieve the WIT point, the rate \eqref{M-eq:R_irs} instead of the DC current \eqref{M-eq:z_irs_approx} should be maximized. In such case, the current expression is dropped and no SCA is involved.
			\end{framed}
			Correspondingly, to achieve the WIT point, the LC-BCD Algorithm~\ref{M-al:lc_bcd} should maximizes $R$ instead of $z$. Line~\ref{li:convergence_begin}--\ref{li:convergence_end} was modified to avoid ambiguity and Algorithm~\ref{M-al:lc_bcd} is indexed below by \ref{al:lc_bcd} .
			\begin{algorithm}[!h]
				\caption{LC-BCD: Waveform and Beamforming.}
				\label{al:lc_bcd}
				\begin{algorithmic}[1]
					\State \textbf{Input} $\beta_2$, $\beta_4$, $\boldsymbol{h}_{\mathrm{D},n}$, $\boldsymbol{V}_{n}$, $P$, $\sigma_n$, $\delta$, $\rho$, $\epsilon$, $\forall n$
					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\phi}^{(0)}$, $\boldsymbol{b}_{\mathrm{I/P},n}^{(0)}$, $\boldsymbol{s}_{\mathrm{I/P}}^{(0)}$, $\forall n$
					\State Set $\boldsymbol{w}_{\mathrm{I/P},n}^{(0)}$, $\forall n$ by \eqref{M-eq:w}
					\State Compute $R^{(0)}$, $z^{(0)}$ by \eqref{M-eq:R_waveform}, \eqref{M-eq:z_waveform}
					\Repeat
						\State $i \gets i + 1$
						\State Get $\boldsymbol{\phi}^{(i)}$ based on $\boldsymbol{w}_{\mathrm{I/P}}^{(i-1)}$ by Algorithm~\ref{M-al:m_sca}
						\State Update $\boldsymbol{h}_n^{(i)}$, $\boldsymbol{b}_n^{(i)}$, $\forall n$ by \eqref{M-eq:h_n}, \eqref{M-eq:b_n}
						\State Update $\boldsymbol{s}_{\mathrm{I}}^{(i)}$, $\boldsymbol{s}_{\mathrm{P}}^{(i)}$ by \eqref{M-eq:s_i}, \eqref{M-eq:s_p}
						\State Update $\boldsymbol{w}_{\mathrm{I/P},n}^{(i)}$, $\forall n$ by \eqref{M-eq:w}
						\State Compute $R^{(i)}$, $z^{(i)}$ by \eqref{M-eq:R_waveform}, \eqref{M-eq:z_waveform}
						\If{$\rho=0$} \label{li:convergence_begin}
							\State $\Delta = R^{(i)} - R^{(i-1)}$
						\Else
							\State $\Delta = z^{(i)} - z^{(i-1)}$
						\EndIf
					\Until $\lvert \Delta \rvert \le \epsilon$ \label{li:convergence_end}
					\State Set $\boldsymbol{\phi}^{\star}=\boldsymbol{\phi}^{(i)}$, $\boldsymbol{w}_{\mathrm{I/P}}^{\star}=\boldsymbol{w}_{\mathrm{I/P}}^{(i)}$
					\State \textbf{Output} $\boldsymbol{\phi}^{\star}$, $\boldsymbol{w}_{\mathrm{I}}^{\star}$, $\boldsymbol{w}_{\mathrm{P}}^{\star}$
				\end{algorithmic}
			\end{algorithm}
			The description on Algorithm~\ref{M-al:lc_bcd} have been updated as follows.
			\begin{framed}
				Note that the BCD algorithm obtains the R-E region by varying the rate constraint from \num{0} to maximum capacity $C_{\max}$\footnotemark, and the LC-BCD algorithm characterizes the R-E tradeoff via two-dimensional search over $\delta$, $\rho$ from \num{0} to \num{1}. For the WIT point, $C_{\max}$ can be obtained in the special case where $\rho=0$ and the objective function becomes $R$ instead of $z$.
			\end{framed}
			\footnotetext{Recall in Remark~\ref{M-re:subband_tradeoff} that passive beamforming enables a resource allocation opportunity at the channel such that different capacities are achievable.}
			\label{re:1.4}
		\end{response}
	\end{reviewer}

@@

			Next, we verify the last observation where the expectation of the DC current scales quartically with $L$ in a much simplified scenario. Consider a SISO WPT system in a frequency-flat channel. We assume a sufficiently large $L$ such that the auxiliary link is dominant and the contribution of direct channel is omitted. With uniform power allocation to multisine ($s_{\mathrm{P},n} = \sqrt{2P}/\sqrt{N}$) in the frequency domain, the DC current writes as
			\begin{equation}
				z_{\mathrm{UP}} = \beta_2 (\Lambda_{\mathrm{I}} \Lambda_{\mathrm{R}} L \lvert X \rvert)^2 P + \frac{3}{8} \beta_4 (\Lambda_{\mathrm{I}} \Lambda_{\mathrm{R}} L \lvert X \rvert)^4 F,
			\end{equation}
			where $\beta_2$ and $\beta_4$ are fixed rectenna parameters, $\Lambda_{\mathrm{I}}$ and $\Lambda_{\mathrm{R}}$ are the path loss of incident and reflected links, $X$ is the random variable that models the small-scale double fading through one IRS element at any subband, and
			\begin{equation}
				F = \sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}} s_{n_1} s_{n_2} s_{n_3} s_{n_4} = \frac{4(2N^2+1)}{3N} P^2.
			\end{equation}
			Taking expectation over $\lvert X \rvert$, we have
			\begin{equation}
				\bar{z}_{\mathrm{UP}} = \beta_2 \Lambda_{\mathrm{I}}^2 \Lambda_{\mathrm{R}}^2 L^2 \mathbb{E}\{\lvert X \rvert^2\} P + \frac{3}{8} \beta_4 \Lambda_{\mathrm{I}}^4 \Lambda_{\mathrm{R}}^4 L^4 \mathbb{E}\{\lvert X \rvert^4\} \frac{2N^2+1}{2N} P^2,
			\end{equation}
			which verifies the scaling order of $L^4$. The analysis is not presented in the manuscript due to the space constraint.
		\end{response}

		\begin{point}
			The authors are suggested to study the impact of IRS passive beamforming on the waveform design without IRS. For example, they can show the optimized waveforms with versus without IRS to unveil the interplay between them. Or even better, analytically compare the two waveforms.
		\end{point}

		\begin{response}
			Thank you for the suggestion. Too see this, we first show one realization of direct channel amplitude (without IRS) and composite channel amplitude (with IRS) for WIT and WPT in Fig.~\ref{fi:channel_amplitude}. It is observed that under the configuration of choice, the WPT-optimized passive beamforming tends to concentrate the channel energy to relatively strong subbands, while the WIT-optimized passive beamforming achieves some balance among all subbands (similar to water-filling at high SNR).

			\begin{figure}[!h]
				\centering
				\resizebox{0.6\columnwidth}{!}{
					\includegraphics{../assets/channel_amplitude}
				}
				\caption{Channel amplitude with and without IRS versus $N$ for $M=1$, $L=100$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{10}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
				\label{fi:channel_amplitude}
			\end{figure}

@@

			On the other hand, the corresponding amplitude of modulated and multisine waveforms are shown in Fig.~\ref{fi:waveform_amplitude}. Note that no multisine is used for WIT and the case is not shown. It is observed that although passive beamforming can enable a flexible resource allocation opportunity at the channel (please refer to Response~\ref{re:2.10} for details), its impact on waveform design is unobvious.

			\begin{figure}[!h]
				\centering
				\subfloat[WIT waveform: modulated]{
				\resizebox{0.32\columnwidth}{!}{
						\input{../assets/waveform_wit_modulated.tex}
					}
				}
				\subfloat[WPT waveform: modulated]{
					\resizebox{0.32\columnwidth}{!}{
						\input{../assets/waveform_wpt_modulated.tex}
					}
				}
				\subfloat[WPT waveform: multisine]{
					\resizebox{0.32\columnwidth}{!}{
						\input{../assets/waveform_wpt_multisine.tex}
					}
				}
				\caption{Sorted modulated and multisine amplitude for WIT and WPT with and without IRS versus $N$ for $M=1$, $L=20$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{10}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
				\label{fi:waveform_amplitude}
			\end{figure}

			We have modified the manuscript as follows to emphasize this point.
			\begin{framed}
				Fig.~\ref{M-fi:channel_amplitude} reveals how passive beamforming influence the channel amplitude and waveform design for one channel realization. \emph{First,} the passive beamforming enables a resource allocation opportunity at the channel as discussed in Remark~\ref{M-re:subband_tradeoff}. Under the specified configuration, the WPT-optimized IRS concentrates channel energy on strong subbands to widen the strength disparity. Correspondingly, the transmit power is focused on strong subbands to improve the energy efficiency, as observed in \ref{M-fi:waveform_wpt_modulated} and \ref{M-fi:waveform_wpt_multisine}. On the other hand, the WIT-optimized IRS provides a fair gain over all subchannels when $L$ is sufficiently large. This is reminiscent of the water-filling scheme at high SNR, but the resource allocation is performed at the channel by passive beamforming. \emph{Second,} the impact of passive beamforming on waveform design is subtle. The amplitude of modulated and multisine waveforms with and without IRS are shown in Figs.~\ref{M-fi:waveform_wit_modulated}--\ref{M-fi:waveform_wpt_multisine}. Note that no multisine is used for WIT and the case is not shown.
			\end{framed}
			\label{re:2.2}
		\end{response}

@@

		\begin{point}
			In the introduction, it is suggested to also discuss the new design challenges posed by the nonlinear model compared to the existing designs under the linear model.
		\end{point}

		\begin{response}
			We believe this is an important issue and have modified the manuscript accordingly as follows.
			\begin{framed}
				\emph{First}, we propose a novel IRS-aided SWIPT architecture based on joint waveform, active and passive beamforming design under the diode nonlinear model proposed in \cite{M-Clerckx2016a}. Although this tractable harvester model accurately reveals how the input power level and waveform shape influence the output DC power, it also introduces design challenges such as frequency compensation (i.e., components of different frequencies compensate and produce DC), waveform coupling (i.e., different waveforms jointly contribute to DC), and non-concavity from high-order objective function.
			\end{framed}
			\label{re:2.3}
		\end{response}

		\begin{point}
			In \ref{M-op:original}, the authors integrated the waveform design and active beamforming design into $\boldsymbol{w}_{\mathrm{I}}$ and $\boldsymbol{w}_{\mathrm{P}}$. However, they separately optimized them later. Is it possible to directly optimize $\boldsymbol{w}_{\mathrm{I}}$ and $\boldsymbol{w}_{\mathrm{P}}$ as a whole?
		\end{point}

### 2021-08-07 main.tex
:pencil: Update manuscript

	\begin{abstract}
		The performance of Simultaneous Wireless Information and Power Transfer (SWIPT) is mainly constrained by the received Radio-Frequency (RF) signal strength. To tackle this problem, we introduce an Intelligent Reflecting Surface (IRS) to compensate the propagation loss and boost the transmission efficiency. This paper proposes a novel IRS-aided SWIPT system where a multi-carrier multi-antenna Access Point (AP) transmits information and power simultaneously, with the assist of an IRS, to a single-antenna User Equipment (UE) employing practical receiving schemes. Considering harvester nonlinearity, we characterize the achievable Rate-Energy (R-E) region through a joint optimization of waveform, active and passive beamforming based on the Channel State Information at the Transmitter (CSIT). This problem is solved by the Block Coordinate Descent (BCD) method, where we obtain the active precoder in closed form, the passive beamforming by the Successive Convex Approximation (SCA) approach, and the waveform amplitude by the Geometric Programming (GP) technique. To facilitate practical implementation, we also propose a low-complexity design based on closed-form adaptive waveform schemes. Simulation results demonstrate the proposed algorithms bring considerable R-E gains with robustness to CSIT inaccuracy and finite IRS states. Results also emphasize the importance of modeling harvester nonlinearity in the IRS-aided SWIPT design.
	\end{abstract}

@@

            The concept of SWIPT was first cast in \cite{Varshney2008}, where the authors investigated the Rate-Energy (R-E) tradeoff for a flat Gaussian channel and typical discrete channels. \cite{Zhou2013} proposed two practical co-located information and power receivers, i.e., Time Switching (TS) and Power Splitting (PS). Dedicated information and energy beamforming were then investigated in \cite{Zhang2013,Park2014} to characterize the R-E region for multi-antenna broadcast and interference channels. On the other hand, \cite{Trotter2009} pointed out that the RF-to-DC conversion efficiency of rectifiers depends on the input power and waveform shape. It implies that the modeling of the energy harvester, particularly its nonlinearity, has a crucial and significant impact on the waveform preference, resource allocation, and system design of any wireless-powered systems \cite{Trotter2009,Clerckx2018,Clerckx2019}. Motivated by this, \cite{Clerckx2016a} derived a tractable nonlinear harvester model based on the Taylor expansion of diode I-V characteristics, then performed joint waveform and beamforming design for WPT. Simulation and experiments showed the benefit of modeling energy harvester nonlinearity in real system design \cite{Kim2019,Kim2020a} and demonstrated the joint waveform and beamforming strategy as a key technique to expand the operation range \cite{Kim2021}. A low-complexity adaptive waveform design by Scaled Matched Filter (SMF) was proposed in \cite{Clerckx2017} to exploit the rectifier nonlinearity, whose advantage is then demonstrated in a prototype with channel acquisition \cite{Kim2017}. Beyond WPT, \cite{Clerckx2018b} uniquely showed that the rectifier nonlinearity brings radical changes to SWIPT design, namely 1) modulated and unmodulated waveforms are not equally suitable for wireless power delivery, 2) a multi-carrier unmodulated waveform superposed to a multi-carrier modulated waveform can enlarge the R-E region of SWIPT, 3) a combination of PS and TS is generally the best strategy, 4) the optimal input distribution is not the conventional Circularly Symmetric Complex Gaussian (CSCG), 5) the rectifier nonlinearity is beneficial to system performance and is essential to efficient SWIPT design. Those observations, validated experimentally in \cite{Kim2019}, led to the question: \emph{What is the optimal input distribution for SWIPT under nonlinearity?} This question was answered in \cite{Varasteh2020} for single-carrier SWIPT, and some attempts were further made in \cite{Varasteh2019d} for multi-carrier SWIPT. The answer sheds new light to the fundamental limits of SWIPT and practical signaling (e.g., modulation and waveform) strategies. It is now well understood from \cite{Clerckx2018b,Varasteh2020,Varasteh2019d} that, due to harvester nonlinearity, a combination of CSCG and on-off keying in single-carrier setting and non-zero mean asymmetric inputs in multi-carrier setting lead to significantly larger R-E region compared to conventional CSCG. Recently, \cite{Varasteh2020a} used machine learning techniques to design SWIPT signaling under nonlinearity to complement the information-theoretic results of \cite{Varasteh2020}, and new modulation schemes were subsequently invented.
		\end{subsection}

		\begin{subsection}{Intelligent Reflecting Surface}
			Intelligent Reflecting Surface (IRS) has recently emerged as a promising technique that adapts the propagation environment to enhance the spectrum and energy efficiency. In practice, an IRS consists of multiple individual sub-wavelength reflecting elements to adjust the amplitude and phase of the incoming signal (i.e., passive beamforming). Different from the relay, backscatter and Frequency-Selective Surface (FSS) \cite{Anwar2018}, the IRS assists the primary transmission using passive components with negligible thermal noise but is limited to frequency-dependent reflection.

			Inspired by the development of real-time reconfigurable metamaterials \cite{Cui2014}, the authors of \cite{Liaskos2018} introduced a programmable metasurface that steers or polarizes the electromagnetic wave at a specific frequency to mitigate signal attenuation. Motivated by this, \cite{Wu2018} proposed an IRS-assisted Multiple-Input Single-Output (MISO) system and jointly optimized the precoder at the Access Point (AP) and the phase shifts at the IRS to minimize the transmit power. The active and passive beamforming problem was then extended to the discrete phase shift case \cite{Wu2019a} and the multi-user case \cite{Wu2019}. In \cite{Abeywickrama2020}, the authors investigated the impact of non-zero resistance on the reflection pattern and emphasized the dependency of the reflection amplitude on the phase shift for practical IRS. To estimate the cascaded AP-IRS-User Equipment (UE) link without RF-chains at the IRS, practical protocols were developed based on element-wise on/off switching \cite{Nadeem2019}, training sequence and reflection pattern design \cite{You2019,Kang2020}, and compressed sensing \cite{Wang2020}. The hardware architecture, design challenges and application opportunities of practical IRS are covered in \cite{Wu2020}. The authors of \cite{Yang2020} considered a novel dynamic passive beamforming for Orthogonal Frequency-Division Multiplexing (OFDM) systems, where the reflection coefficient is varied over consequent time slots to enable flexible resource allocation over time-frequency Resource Blocks (RBs). In \cite{Dai2020}, a prototype IRS with \num{256} \num{2}-bit elements based on Positive Intrinsic-Negative (PIN) diodes was developed to support real-time high-definition video transmission at \si{GHz} and mmWave frequency. Deep reinforcement learning tools were also applied in \cite{Yang2021} to assist practical secure beamforming and reflection pattern design under QoS constraints for time-varying channels.
		\end{subsection}

		\begin{subsection}{IRS-Aided SWIPT}
			In IRS-aided SWIPT, the effective channel enhancement can improve the end-to-end energy efficiency and the smart reflection control can enhance the R-E tradeoff. For multi-user IRS-aided SWIPT systems, dedicated energy beams were proved unnecessary for the Weighted Sum-Power (WSP) maximization \cite{Wu2020b} but essential when fairness issue is considered \cite{Tang2019}. It was also claimed that Line-of-Sight (LoS) links could boost the WSP as rank-deficient channels tend to require fewer energy beams \cite{Wu2020a}. However, \cite{Wu2020b,Tang2019,Wu2020a} were based on an inaccurate linear energy harvester model that is known in both the RF and the communication literature to be inefficient and inaccurate \cite{Clerckx2019,Trotter2009,Clerckx2018,Clerckx2016a,Kim2019,Kim2020a,Kim2021,Clerckx2017,Kim2017,Clerckx2018b,Varasteh2020,Varasteh2019d,Varasteh2020a}. In \cite{Xu2021}, the authors proposed a scalable resource allocation framework for SWIPT systems involving large-scale IRS, where the reflectors are grouped into tiles and the optimization process is divided into an offline mode-design stage and an online mode-selection stage. It was concluded that the proposed two-stage algorithm not only enables a flexible balance between performance and complexity but also adapts well to practical IRS and harvester models. A recent tutorial paper \cite{Wu2021c} provided a comprehensive overview on IRS-aided wireless-powered networks, where channel estimation, resource allocation and practical constraints are discussed in detail. To the best of our knowledge, all existing papers considered resource allocation and beamforming design for dedicated information and energy users in a single-carrier network. In this paper, we instead build our design based on a proper nonlinear harvester modeling that captures the dependency of the output DC power on both the power and shape of the input waveform, and marry the benefits of joint multi-carrier waveform and active beamforming optimization for SWIPT with the passive beamforming capability of IRS, to investigate the R-E tradeoff for one SWIPT user with practical co-located information decoder and energy harvester. We ask ourselves the important question: \emph{How to jointly exploit the spatial domain and the frequency domain efficiently through joint waveform and beamforming design to enlarge the R-E region of IRS-aided SWIPT?} The contributions of this paper are summarized as follows.

>>>>

	\begin{abstract}
		The performance of Simultaneous Wireless Information and Power Transfer (SWIPT) is mainly constrained by the received Radio-Frequency (RF) signal strength. To tackle this problem, we introduce an Intelligent Reflecting Surface (IRS) to compensate the propagation loss and boost the transmission efficiency. This paper proposes a novel IRS-aided SWIPT system where a multi-carrier multi-antenna Access Point (AP) transmits information and power simultaneously, with the assist of an IRS, to a single-antenna User Equipment (UE) employing practical receiving schemes. Considering harvester nonlinearity, we characterize the achievable Rate-Energy (R-E) region through a joint optimization of waveform, active and passive beamforming based on the Channel State Information at the Transmitter (CSIT). This problem is solved by the Block Coordinate Descent (BCD) method, where we obtain the active precoder in closed form, the passive beamforming by the Successive Convex Approximation (SCA) approach, and the waveform amplitude by the Geometric Programming (GP) technique. To facilitate practical implementation, we also propose a low-complexity design based on closed-form adaptive waveform schemes. Simulation results demonstrate the proposed algorithms bring considerable R-E gains with robustness to CSIT inaccuracy and finite IRS states, and emphasize the importance of modeling harvester nonlinearity in the IRS-aided SWIPT design.
	\end{abstract}

@@

            The concept of SWIPT was first cast in \cite{Varshney2008}, where the authors investigated the Rate-Energy (R-E) tradeoff for a flat Gaussian channel and typical discrete channels. \cite{Zhou2013} proposed two practical co-located information and power receivers, i.e., Time Switching (TS) and Power Splitting (PS). Dedicated information and energy beamforming were then investigated in \cite{Zhang2013,Park2014} to characterize the R-E region for multi-antenna broadcast and interference channels. On the other hand, \cite{Trotter2009} pointed out that the RF-to-DC conversion efficiency of rectifiers depends on the input power and waveform shape. It implies that the modeling of the energy harvester, particularly its nonlinearity, has a crucial impact on the waveform preference, resource allocation, and system design of any wireless-powered systems \cite{Trotter2009,Clerckx2018,Clerckx2019}. Motivated by this, \cite{Clerckx2016a} derived a tractable nonlinear harvester model based on the Taylor expansion of diode I-V characteristics, and performed joint waveform and beamforming design for WPT. Simulation and experiments showed the benefit of modeling energy harvester nonlinearity in real system design \cite{Kim2019,Kim2020a} and demonstrated the joint waveform and beamforming strategy as a key technique to expand the operation range \cite{Kim2021}. A low-complexity adaptive waveform design by Scaled Matched Filter (SMF) was proposed in \cite{Clerckx2017} to exploit the rectifier nonlinearity, whose advantage is then demonstrated in a prototype with channel acquisition \cite{Kim2017}. Beyond WPT, \cite{Clerckx2018b} uniquely showed that the rectifier nonlinearity brings radical changes to SWIPT design, namely 1) modulated and unmodulated waveforms are not equally suitable for wireless power delivery; 2) a multi-carrier unmodulated waveform superposed to a multi-carrier modulated waveform can enlarge the R-E region; 3) a combination of PS and TS is generally the best strategy; 4) the optimal input distribution is not the conventional Circularly Symmetric Complex Gaussian (CSCG); 5) modeling rectifier nonlinearity is beneficial to system performance and is essential to efficient SWIPT design. Those observations, validated experimentally in \cite{Kim2019}, led to the question: \emph{What is the optimal input distribution for SWIPT under nonlinearity?} This question was answered in \cite{Varasteh2020} for single-carrier SWIPT, and some attempts were further made in \cite{Varasteh2019d} for multi-carrier SWIPT. The answer sheds new light to the fundamental limits of SWIPT and practical signaling (e.g., modulation and waveform) strategies. It is now well understood from \cite{Clerckx2018b,Varasteh2020,Varasteh2019d} that, due to harvester nonlinearity, a combination of CSCG and on-off keying in single-carrier setting and non-zero mean asymmetric inputs in multi-carrier setting lead to significantly larger R-E region compared to conventional CSCG. Recently, \cite{Varasteh2020a} used machine learning techniques to design SWIPT signaling under nonlinearity to complement the information-theoretic results of \cite{Varasteh2020}, and new modulation schemes were subsequently invented.
		\end{subsection}

		\begin{subsection}{Intelligent Reflecting Surface}
			Intelligent Reflecting Surface (IRS) has recently emerged as a promising technique that adapts the propagation environment to enhance the spectrum and energy efficiency. In practice, an IRS consists of multiple individual sub-wavelength reflecting elements to adjust the amplitude and phase of the incoming signal (i.e., passive beamforming). Different from the relay, backscatter and frequency-selective surface \cite{Anwar2018}, the IRS assists the primary transmission using passive components with negligible thermal noise but is limited to frequency-dependent reflection.

			Inspired by the development of real-time reconfigurable metamaterials \cite{Cui2014}, the authors of \cite{Liaskos2018} introduced a programmable metasurface that steers or polarizes the electromagnetic wave at a specific frequency to mitigate signal attenuation. \cite{Wu2018} proposed an IRS-assisted Multiple-Input Single-Output (MISO) system and jointly optimized the precoder at the Access Point (AP) and the phase shifts at the IRS to minimize the transmit power. The active and passive beamforming problem was then extended to the discrete phase shift case \cite{Wu2019a} and the multi-user case \cite{Wu2019}. In \cite{Abeywickrama2020}, the authors investigated the impact of non-zero resistance on the reflection pattern and emphasized the coupling between reflection amplitude and phase shift for practical IRS. To estimate the cascaded AP-IRS-User Equipment (UE) link without RF-chains at the IRS, practical protocols were developed based on element-wise on/off switching \cite{Nadeem2019}, training sequence and reflection pattern design \cite{You2019,Kang2020}, and compressed sensing \cite{Wang2020}. The hardware architecture, design challenges and application opportunities of practical IRS are covered in \cite{Wu2020}. In \cite{Dai2020}, a prototype IRS with \num{256} \num{2}-bit elements based on Positive Intrinsic-Negative (PIN) diodes was developed to support real-time high-definition video transmission at \si{GHz} and mmWave frequency.
		\end{subsection}

		\begin{subsection}{IRS-Aided SWIPT}
			By integrating IRS with SWIPT, its smart and effective reflection can enhance the R-E tradeoff and improve the end-to-end power efficiency. For multi-user IRS-aided SWIPT systems, dedicated energy beams were proved unnecessary for the Weighted Sum-Power (WSP) maximization \cite{Wu2020b} but essential when fairness issue is considered \cite{Tang2019}. It was also claimed that Line-of-Sight (LoS) links could boost the WSP since rank-deficient channels require fewer energy beams \cite{Wu2020a}. However, \cite{Wu2020b,Tang2019,Wu2020a} were based on an inaccurate linear energy harvester model that is known in both the RF and the communication literature to be inefficient and inaccurate \cite{Clerckx2019,Trotter2009,Clerckx2018,Clerckx2016a,Kim2019,Kim2020a,Kim2021,Clerckx2017,Kim2017,Clerckx2018b,Varasteh2020,Varasteh2019d,Varasteh2020a}. Based on practical IRS and energy harvester models, \cite{Xu2021c} introduced a scalable resource allocation framework for a large-scale tile-based IRS-assisted SWIPT system, where the optimization is divided into a reflection mode design stage and a joint reflection mode selection and precoder design stage. The proposed framework provides a flexible balance between performance and complexity. To the best of our knowledge, all existing papers considered resource allocation and beamforming design for dedicated information and energy users in a single-carrier network. In this paper, we instead build our design based on a proper nonlinear harvester modeling that captures the dependency of the output DC power on both the power and shape of the input waveform, and marry the benefits of joint multi-carrier waveform and active beamforming optimization for SWIPT with the passive beamforming capability of IRS, to investigate the R-E tradeoff for one SWIPT user with practical co-located information decoder and energy harvester. We ask ourselves the important question: \emph{How to jointly exploit the spatial domain and the frequency domain efficiently through joint waveform and beamforming design to enlarge the R-E region of IRS-aided SWIPT?} The contributions of this paper are summarized as follows.

			\emph{First,} we propose a novel IRS-aided SWIPT architecture based on joint waveform, active and passive beamforming design under the diode nonlinear model in \cite{Clerckx2016a}. Although this tractable harvester model accurately reveals how the input power level and waveform shape influence the output DC power, it also introduces design challenges such as frequency coupling (i.e., components of different frequencies compensate and produce DC), waveform coupling (i.e., different waveforms jointly contribute to DC), and high-order objective function. To make an efficient use of the rectifier nonlinearity, we superpose a multi-carrier unmodulated power waveform (deterministic multisine) to a multi-carrier modulated information waveform and evaluate the performance under the TS and PS receiving modes. The proposed joint waveform, active and passive beamforming architecture exploits across frequency and spatial domains the rectifier nonlinearity, the channel selectivity, and a beamforming gain to enlarge the achievable R-E region. This is the first paper to propose a joint waveform, active and passive beamforming architecture for IRS-aided SWIPT.
